Synthesizing Symmetric Lenses

### 2018-06-04 papers/SymmetricLenses/main.tex
add stuff

    \Function{GreedySeqSynth}{$\Examples,\SequenceOf{\String_0\SeqSep\Atom_1\SeqSep\ldots\SeqSep\Atom_n\SeqSep\String_n},\SequenceOf{\StringAlt_0\SeqSep\AtomAlt_1\SeqSep\ldots\SeqSep\AtomAlt_m\SeqSep\String_m}$}
    \If{$\Call{CannotMap}{\Examples,\SequenceOf{\String_0\SeqSep\Atom_1\SeqSep\ldots\SeqSep\Atom_n\SeqSep\String_n},\SequenceOf{\StringAlt_0\SeqSep\AtomAlt_1\SeqSep\ldots\SeqSep\AtomAlt_m\SeqSep\String_m}}$}
    \State $\ReturnVal{\None}$
    \EndIf
    \State $\ALS \gets
    \Call{\CartesianMap}{\AtomSynth(\Examples),\ListOf{\Atom_1;\ldots;\Atom_n},\ListOf{\AtomAlt_1;\ldots;\AtomAlt_m}}$
    \State $\GreedyState \gets \Call{GreedySeqState.Init}{\ALS}$
    \While{$\Call{GreedySeqState.Continue}{\GreedyState}$}
    \State $(\GreedyState,\SAtomLens) \gets
    \Call{GreedySeqState.PopBest}{\GreedyState}$
    \If{$\Call{GreedySeqState.UsefulAdd}{\GreedyState,\SAtomLens}
      \BooleanOr \Call{NecessaryAdd}{\Examples,\SAtomLens}$}
    \State $\GreedyState \gets \Call{GreedyState.AddAtom}{\GreedyState,\SAtomLens}$
    \EndIf
    \EndWhile
    \ReturnVal{\Call{GreedyState.ToDNFLens}{\GreedyState}}
    \EndFunction
  \end{algorithmic}
\end{algorithm}

\paragraph*{Symmetric Sequence lenses} Algorithm~\ref{alg:greedyseqsynth}
presents \GreedySeqSynth, a means to synthesizes symmetric sequence lenses. This
algorithm uses \PCF{AtomSynth}, a simple function that synthesizes atom lenses
by iterating the DNF lens between its subcomponents. The inputs to
\GreedySeqSynth are a pair of stochastic atoms and a suite of input-output
examples. First, \PCF{CannotMap} checks if there is a possibility of a lens
between the given sequences regular expressions that is consistent with the
examples. If there is not, \GreedySeqSynth returns \None early. After this,
\GreedySeqSynth finds the best lenses between each atom pair of the left and
right sequences. An internal state for the algorithm is initialized from these.
This state consists of two things: an intermediate partial sequence lens and a
priority queue consisting of potential sequence lenses.  On initialization,
\GreedySeqSynth throws all the atom lenses into the priority queue.

\GreedySeqSynth then loops until there are no more atom lenses in the priority
queue. Within this loop, atom lenses are popped. The atom lens is then added if
it is either necessary, or useful. Within a sequence lens, each atom can either
be projected or be synchronized with exactly one atom in the other sequence.
Certain atoms need to be mapped, for example if a put changes the data of that
field. In such situations, an atom lens is necessary. A useful atom lens is
where adding that lens reduces the overall cost of the partial lens. If adding
that lens requires removing another lens, where the added cost by removing that
other lens is more than is removed by adding the proposed lens. Finally, after
all atoms have been popped, the partial sequence lens is converted into a
symmetric DNF lens. This is only possible if all atoms that need to be mapped,
are: if they are not, \PCF{GreedyState.ToDNFLens} instead returns \None.

>>>>

    \Function{GreedySeqSynth}{$\Examples,\SequenceOf{\String_0\SeqSep\Atom_1\SeqSep\ldots\SeqSep\Atom_n\SeqSep\String_n},\SequenceOf{\StringAlt_0\SeqSep\AtomAlt_1\SeqSep\ldots\SeqSep\AtomAlt_m\SeqSep\String_m}$}
    \If{$\Call{CannotMap}{\Examples,\SequenceOf{\String_0\SeqSep\Atom_1\SeqSep\ldots\SeqSep\Atom_n\SeqSep\String_n},\SequenceOf{\StringAlt_0\SeqSep\AtomAlt_1\SeqSep\ldots\SeqSep\AtomAlt_m\SeqSep\String_m}}$}
    \State $\ReturnVal{\None}$
    \EndIf
    \State $\ALS \gets
    \Call{\CartesianMap}{\AtomSynth(\Examples),\ListOf{\Atom_1;\ldots;\Atom_n},\ListOf{\AtomAlt_1;\ldots;\AtomAlt_m}}$
    \State $\GreedyState \gets \Call{GreedySeqState.Init}{\ALS}$
    \While{$\Call{GreedySeqState.Continue}{\GreedyState}$}
    \State $(\GreedyState,\SAtomLens) \gets
    \Call{GreedySeqState.PopBest}{\GreedyState}$
    \If{$\Call{GreedySeqState.UsefulAdd}{\GreedyState,\SAtomLens}
      \BooleanOr \Call{NecessaryAdd}{\Examples,\SAtomLens}$}
    \State $\GreedyState \gets \Call{GreedySeqState.AddAtom}{\GreedyState,\SAtomLens}$
    \EndIf
    \EndWhile
    \ReturnVal{\Call{GreedySeqState.ToDNFLens}{\GreedyState}}
    \EndFunction
  \end{algorithmic}
\end{algorithm}

\paragraph*{Symmetric Sequence lenses} Algorithm~\ref{alg:greedyseqsynth}
presents \GreedySeqSynth, a means to synthesizes symmetric sequence lenses. This
algorithm uses \PCF{AtomSynth}, a simple function that synthesizes atom lenses
by iterating the DNF lens between its subcomponents. The inputs to
\GreedySeqSynth are a pair of stochastic atoms and a suite of input-output
examples. First, \PCF{CannotMap} checks if there is a possibility of a lens
between the given sequences regular expressions that is consistent with the
examples. If there is not, \GreedySeqSynth returns \None early. After this,
\GreedySeqSynth finds the best lenses between each atom pair of the left and
right sequences. An internal state for the algorithm is initialized from these.
This state consists of two things: an intermediate sequence lens and a priority
queue consisting of potential sequence lenses. On initialization,
\GreedySeqSynth throws all the atom lenses into the priority queue, and the
intermediate sequence lens is one that projects all the atoms.

\GreedySeqSynth then loops until there are no more atom lenses in the priority
queue. Within this loop, atom lenses are popped. The atom lens is then added if
it is either necessary, or useful. Within a sequence lens, each atom can either
be projected or be synchronized with exactly one atom in the other sequence, and
examples can show that certain atoms \emph{need} to be mapped. In such
situations, that atom lens is necessary. A useful atom lens is where adding that
lens reduces the overall cost of the partial lens. If both atoms are not
involved in an atom lens, the lens will always be useful, but sometimes adding
that lens requires removing another lens. If the cost added by removing that
other lens is more than is removed by adding the proposed lens, then this atom
lens is not included in the sequence lens. Finally, after all atoms have been
popped, the sequence lens is validated and returned. The sequence lens is
validated if all atoms that need to be mapped, are: if they are not,
\PCF{GreedySeqState.ToDNFLens} instead returns \None.
